\documentclass[]{aanguyen_cv}

\usepackage{fontawesome}
\usepackage{xcolor}

\begin{document}
	\header{ANDREW}{NGUYEN}{electrical engineering candidate}
	\begin{sidebar}%
		\vspace{35pt}% space between top and sidebar
		\section{Contact}
			\iconentry{\faEnvelope}{andrew.nguyen@uwaterloo.ca}
			\iconentry{\faPhone}{(647)-918-4240}
			%\iconentry{\faHome}{website would go here}
			\iconentry{\faGithub}{github.com/aanguyen}
			\iconentry{\faLinkedin}{linkedin.com/in/aanguyen}
			\vspace{0.65cm}%
		\section{Skills}
			\textbf{Conversationally Fluent: }Java, C++, HTML5, CSS3
			\textbf{Working Knowledge: }R, VisualBasic, Arduino, \LaTeX
			\textbf{Curious Tourist: }JavaScript, Python, Node.js
			\vspace{0.65cm}%
		\section{Education}
			\eduentry%
				{University of Waterloo}%
				{Candidate for B. A. Sc., Electrical\\Engineering}%
				{2016 - Present}%
				{Fall 2016 Average: 90\% (Top Decile)\\Dean's Honour List}
			\vspace{0.65cm}%
		\section{Awards}
			\awardentry{2017}{US Computing Olympiad Gold Division}%
			\awardentry{2016}{Nortel Networks Undergraduate Scholarship}%
			\awardentry{2016}{University of Waterloo\\President's Scholarship of Distinction}%
			\awardentry{2016}{Top 5\% on AMC12 (AIME Qualifier)}%
			\awardentry{2016}{2nd place nationally at ARML}%
			\vspace{0.65cm}%
		\section{Interests}
		%\begin{itemize}%
		%	\item Something
		%\end{itemize}%
		$\bullet$ Athletics - ice hockey, volleyball, soccer
		$\bullet$ Music - guitar, saxophone, piano
		$\bullet$ Languages - French, Spanish, Vietnamese
		$\bullet$ Machine learning, big data
		$\bullet$ Cooking, baking (still a beginner)
	\end{sidebar}%
	\begin{main}%
		\vspace{35pt}%
		\section{Experience}
			\mainentry%
				{Junior Software Engineer}%
				{Ottawa, Ontario}%
				{Industry Canada}%
				{Jan 2017 - Present}%
				{Added functionality to spectrum measurement software in Visual Basic, and performed data analysis and visualization of Wi-Fi signal strengths in R. Performed basic hardware tests to ensure smooth integration with software components.}
			\mainentry%
				{Computer Camp Counsellor}%
				{North York, Ontario}%
				{City of Toronto}%
				{May 2015 - Aug 2015}%
				{Taught campers aged 6-12 basic computer skills including Word, Excel, Powerpoint, and touch typing. Resolved conflicts between campers and kept order, both in the community centre and while on off-site field trips around Toronto.}
			\mainentry%
				{Assistant Math Teacher}%
				{Toronto, Ontario}%
				{Spirit of Math Schools}%
				{Sep 2013 - Jun 2015}%
				{Assisted teacher in explaining theoretical and applied concepts to the class, as well as working with individual students to provide more focused help when needed. Represented the Spirit of Math organization professionally whilst dealing with parents.}
			\vspace{0.65cm}%
		\section{Projects}
			\mainentry%
				{SignBuddy{\faGithub}}%
				{CUHacking I}%
				{github.com/aanguyen/SignBuddy}%
				{Mar 2017}%
				{Interactive sign language recognizer powered by machine learning using a Leap Motion controller, incorporated into a web video chat client. Built with Python and HTML/CSS/JavaScript.}
			\mainentry%
				{CollaboPiano {\faGithub}}%
				{IEEE Hardware Hackathon}%
				{github.com/aanguyen/collaboPiano}%
				{Feb 2017}%
				{Two piano simulators that play identical sound on each speaker as an aggregate of both pianos, allowing users to collaborate on the same music from afar. Built with a pair of Arduino Unos, transceivers, and force sensors as the keys.}
			\mainentry%
				{TherapyHelper {\faGithub}}%
				{DeltaHacks III}%
				{github.com/dtong1113/TherapyHelper}%
				{Jan 2017}%
				{Web application giving therapists a way to both provide custom self-assessments and view all patient data in one place, as well as giving patients a more convenient way to complete their homework. Built with JavaScript, Vue.js, Node.js, and standard HTML/CSS.}
			\mainentry%
				{Web Robot {\faGithub}}%
				{ConU Hacks II}%
				{github.com/Havkiin/RobotRock}%
				{Jan 2017}%
				{Robot controlled through user input from a website, that can capture/save images on click without requiring an internet connection. Built with Arduino and PHP, as well as standard HTML/CSS.}
			%\mainentry%
			%	{Basic Assembly Simulator {\faGithub}}%
			%	{ECE150}%
			%	{github.com/aanguyen/assembly-parser}%
			%	{Nov 2016}%
			%	{A simple parser of RISC assembly instructions, and a customized priority queue (without using library functions) to push events based on the required completion time and pop from the beginning, built with C++.}
			\vspace{0.65cm}%
	\end{main}%
\end{document}

